Estimating epidemiological quantities from repeated cross-sectional prevalence measurements

### 2022-02-21 docs/paper.Rmd
prettier table and move figures

```{r prevalence-plot, out.width=".7\\paperwidth", fig.cap = "Model posteriors for England. A. Estimates of daily modelled prevalence and modelled prevalence as published by ONS. B. Estimated incidence of new infections. C. Estimated antibody prevalence and estimes as published by ONS. D. Estimated reproduction numbers."}
knitr::include_graphics(here::here("figures", "readme", "example-estimates.png"))
```

@@

```{r params-table}
biol_params %>%
  kbl(caption = "90% credible intervals (as quantiles of the posterior distribution) of biological parameters.",
      booktabs = TRUE)
```

@@

```{r pairs-plot, out.width=".7\\paperwidth", fig.cap = "Scatter plots and histograms of posterior parameter samples."}
knitr::include_graphics(here::here("figures", "readme", "pairs.png"))
```

>>>>

```{r prevalence-plot, out.width=".7\\paperwidth", fig.cap = "Model posteriors for England. A. Estimates of daily modelled prevalence and modelled prevalence as published by ONS. B. Estimated incidence of new infections. C. Estimated antibody prevalence and estimes as published by ONS. D. Estimated reproduction numbers."}
knitr::include_graphics(here::here("figures", "example", "example-estimates.png"))
```

@@

```{r params-table}
biol_params %>%
  kbl(caption = "90% credible intervals (as quantiles of the posterior distribution) of biological parameters.",
      booktabs = TRUE) %>%
  kable_styling()
```

@@

```{r pairs-plot, out.width=".7\\paperwidth", fig.cap = "Scatter plots and histograms of posterior parameter samples."}
knitr::include_graphics(here::here("figures", "example", "pairs.png"))
```
